\Huge Conferences in the Era of Expensive Carbon

### 2019-06-05 main.tex
Bit more writing

\SECTION{Putting a Price on Carbon}

Fortunately, there is a well-established mechanism for comparing apples and
oranges (indeed, for comparing almost anything): the magic of markets.  By
mapping choices and preferences in disparate domains to a common scale
(namely money), economic markets can be viewed as massively distributed
computations that balance costs an benefits across vastly different
activities.\bcp{Give a simple, concrete example.}  For this reason, many
policy experts advocate addressing climate change through some form of
carbon pricing, which places a monetary cost on greenhouse gas emissions,
thus giving a market signal that changes aggregate behavior.\bcp{See
  https://kleinmanenergy.upenn.edu/policy-digests/why-carbon-pricing-falls-short
  for lots of good phrasing and citations.}  Exactly how the price of carbon
should be set is a challenging policy question, but it has a clear goal: The
cost should be set so that the world arrives at zero emissions within the
timeframe that climate scientists tell us is safe.

In the long term, a carbon price should be uniform across society---i.e., it
should be imposed by governments.  Indeed, many countries\bcp{e.g.?} and
states (e.g., California) have already adopted carbon pricing policies; more
will follow.
%
Bottom line: We are entering an era in which carbon will be expensive.

Expecting that this era is coming, what should we rationally do now to
ensure that ACM, and computer-science research broadly, continue to thrive
in a world where air travel is more expensive?  Believing that it needs to
come as quickly as possible to avert disaster, what can we do to accelerate
the process? \mwh{The question now seems to have changed. The paper started by
  saying ACM has an ``especially important role to play,'' but now
  seems to suggest it should be reacting to an inevitable/coming
  future. These questions probably need to go much earlier, and the earlier
  text reworked around them.}

>>>>

\SECTION{Putting a Price on Emissions}

Fortunately, there is a well-established mechanism for comparing apples and
oranges---indeed, for comparing almost anything!  Economists call it ``the
magic of markets.''  By mapping choices and preferences in disparate domains
onto a common scale (money), economic markets can be viewed as massively
distributed computations that optimize costs and benefits across vastly
different activities.\bcp{Give a simple, concrete example.}  For this
reason, many policy experts advocate addressing climate change through some
form of carbon pricing, which places a monetary cost on greenhouse gas
emissions, sending a clear market signal that changes aggregate
behavior.\bcp{See
  https://kleinmanenergy.upenn.edu/policy-digests/why-carbon-pricing-falls-short
  for lots of good phrasing and citations.}  Exactly how the price of carbon
should be set is a challenging policy question, but it has a clear goal: It
should be chosen so that the world arrives at zero emissions within the
timeframe that climate scientists tell us is safe.

To be effective in the long term, a carbon price needs to be uniform across
society---i.e., it should be imposed by governments.  Indeed, many
countries\bcp{e.g.?} and states (e.g., California) have already adopted
carbon pricing policies; more will follow.
%
Bottom line: We are entering an era in which carbon will be expensive.

Anticipating this era, what should we rationally do now to ensure that ACM,
and computer-science research more broadly, continue to thrive in a world
where air travel is more expensive?  Believing that it needs to come quickly
to avert disaster, what can we do to accelerate the process? \mwh{The
  question now seems to have changed. The paper started by saying ACM has an
  ``especially important role to play,'' but now seems to suggest it should
  be reacting to an inevitable/coming future. These questions probably need
  to go much earlier, and the earlier text reworked around them.}
